---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ProteoBayes

<!-- badges: start -->
<!-- badges: end -->

The goal of ProteoBayes is to ...

## Installation

You can install the released version of ProteoBayes from CRAN with:

```{r eval = FALSE}
install.packages("ProteoBayes")
```

You can install the development version of ProteoBayes like so:

```{r}
# install.packages("devtools")
devtools::install_github("mariechion/ProteoBayes")
```


## ProteoBayes in a nutshell

Generate a synthetic proteomic dataset with the correct format:

```{r simu data}
library(ProteoBayes)
set.seed(42)

## Generate a dataset without imputations
data = simu_db()

## Generate a dataset with multiple imputations
data_imp = simu_db(multi_imp = TRUE)

data
data_imp
```

The parameters of all posterior distributions can be computed thanks to:

```{r compute posteriors}

post = posterior_mean(data)

post

```

When considering Peptides independently (no inter-Peptides correlations), the method is unaffected by missing values and no imputation is necessary.  


We can also consider correlations between Peptides by using a multivariate version of the method. In this context, missing values need to be imputed beforehand (multiple imputations is accepted), and the dedicated function is:

```{r compute posteriors multi}
post_imp = multi_posterior_mean(data_imp)

post
```

Once parameters of the posterior distributions are available. We can sample from those distributions and visualise the differences between any groups for each peptide by using: 

```{r visualisation}

sample = sample_distrib(post)

plot_distrib(sample, group1 = 1, group2 = 2, peptide = 'Peptide_1' )

```

When comparing a large number of Peptides simultaneously, the function `identify_diff()` can be used to check for probable differences between groups 
for each Peptide:

```{r identify differences}
identify_diff(post)

```

